Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.

### 2015-06-03 papers/data_paper/datapaper.tex
final

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 0821.}
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 1332.}
  \end{center}
  \end{figure}

>>>>

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 0821.
  NGC 0821 is an edge-on elliptical/lenticular galaxy. 
  The ellipticity profile and the velocity map show the presence of a faint intermediate-scale disk. 
  Given its edge-on inclination, the disk is modeled with a low-$n$ S\'ersic function.   
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 0821.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-id + PSF-n & $36.8$  &  $5.4$ \\
  T.W. 1D eq.  & S-bul + e-id + PSF-n & $20.7$  &  $6.0$ \\
  T.W. 2D      & S-bul + e-id + m-n   & $33.8$  &  $2.5$ \\
  \hline
  GD07    & S-bul 		 & $44.1$   &  $4.0$ \\           
  S+11    & S-bul 		 & $63.6$   &  $7.0$ \\           
  B+12    & S-bul 		 & $111.3$  &  $7.7$ \\           
  L+14    & S-bul + e-d + S-halo & $3.8$    &  $3.1$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n0821}
  \tablecomments{
  L+14 obtained the smallest estimates of the spheroid effective radius and S\'ersic index because they failed to identify the extent 
  of the intermediate-scale disk. 
  Inaccurate sky subtraction could be the reason why B+12 obtained a large estimate of the effective radius.
  }
  \end{table}

@@

  Our equivalent-axis decomposition returns a spheroidal component accounting for 95\% of the total light,
  and an embedded disk accounting for the remaining 5\%.
  In passing, we note that the bulge-disk decomposition performed by \citet{rusli2011} on NGC 1332 
  is significantly different from our best-fit model.
  \citet{rusli2011} did not identify an intermediate-scale embedded disk, 
  but instead proposed a model featuring a S\'ersic bulge ($n_{\rm sph} \sim 2.3$, $R_{\rm e,sph} \sim 8''$), accounting for 43\% of the total light, 
  and a large-scale exponential disk. 
  This result led them to the conclusion that NGC 1332 is a disk dominated lenticular galaxy 
  and is displaced from the $M_{\rm BH} - L_{\rm K,sph}$ (black hole mass vs. $K$-band spheroid luminosity) relation of \citet{marconihunt2003} 
  by an order of magnitude along the $M_{\rm BH}$ direction.
  Assuming instead that, as follows from our model, 
  the galaxy spheroid is a factor of two more luminous than what claimed by \citet{rusli2011}, 
  NGC 1332 would no longer be an outlier in our $M_{\rm BH} - L_{\rm sph}$ diagram. \\

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 1332.
  NGC 1332 is an edge-on elliptical/lenticular galaxy. 
  Given its large stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
  The ellipticity profile proves the presence of an intermediate-scale disk. 
  Given the edge-on inclination of such disk, we model it with a low-$n$ S\'ersic profile. 
  The data within the innermost $6''.1$ are excluded from the fit.
  }
  \end{center}
  \end{figure}
